The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-03-27 VegOzone.tex
Added suggestions by Frode.

\subsection{NIBIO research station Svanhovd}
\label{subsec:svanhovd}
"Svanhovd is located beside the Pasvik river, in the middle of the wedge of Norwegian land separating Russia and Finland in the north. It is where the eastern Siberian taiga meets the western Boreal forest. [...] Svanhovd was originally established as a State Demonstration and Experimental Farm in the 1930's, in order to expand agriculture in Pasvik valley [...]" - \href{https://www.nibio.no/en/about-eng/addresses/northern-norway/svanhovd}{NIBIO}.\\
The research station at Svanhovd comprises long-term observations of various agrameteorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global radiation, and soil moisture and temperature at different depths. For the purpose of relating observed damage on ozone sensitive plants (e.g. clover and tobacco) an ozone monitor had been installed during the growing seasons 2018/19). The relevant data are described in more detail Section~\ref{subsubsec:atmo_svanvik}.
Note that from 1986--1996, ozone monitoring has been conducted operationally at Svanhovd. Details about these historical ozone data will be given in Section~\ref{subsubsec:ebas}.\\
The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the NIBIO research station are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. 
\emph{Comment: Invite co-authors from NILU and NIBIO?}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{station_map_fennoscandia}
  \caption{Cap of the North. Locations of past and present ozone observation sites in northern Fennoscandia used within this study. For more details see Tab.~\ref{tab:ebas_obs}.}
  \label{fig:station_map_fennoscandia}
\end{figure}

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from NILU EBAS database except for the data for the 2018/19 growing season at Svanhovd. In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking.

>>>>

\subsection{NIBIO research station Svanhovd}
\label{subsec:svanhovd}
"Svanhovd is located beside the Pasvik river, in the middle of the wedge of Norwegian land separating Russia and Finland in the north. It is where the eastern Siberian taiga meets the western Boreal forest. [...] Svanhovd was originally established as a State Demonstration and Experimental Farm in the 1930's, in order to expand agriculture in Pasvik valley [...]" - \href{https://www.nibio.no/en/about-eng/addresses/northern-norway/svanhovd}{NIBIO webpage, accessed March 2020}.\\
The research station at Svanhovd comprises long-term observations of various agrameteorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global radiation, and soil moisture and temperature at different depths. For the purpose of relating observed damage on ozone sensitive plants (e.g. clover and tobacco) an ozone monitor had been installed during the growing seasons 2018/19). The relevant data are described in more detail Section~\ref{subsubsec:atmo_svanvik}.
Note that from 1986--1996, ozone monitoring has been conducted operationally at Svanhovd. Details about these historical ozone data will be given in Section~\ref{subsubsec:ebas}.\\
The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the NIBIO research station are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. 
\emph{Comment: Invite co-authors from NILU and NIBIO?}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{station_map_fennoscandia}
  \caption{Cap of the North. Locations of past and present ozone observation sites in northern Fennoscandia used within this study. For more details see Tab.~\ref{tab:ebas_obs}. The same color coding for each station as displayed herein will be used in all following figures.}
  \label{fig:station_map_fennoscandia}
\end{figure}

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from NILU EBAS database. Data for the 2018/19 growing season at Svanhovd have not yet been made available \emph{alternative: shall be made available at a later point}. In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking.
